---
title: "HLSA hits in schizophrenia studies"
author: "Ilea Eskildsen Heft"
date: "March 8, 2016"
output: word_document
---

### RNA-Seq

```{r echo=FALSE}
wu.12 <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-schiz/wu-2012/wu-12-supp-table-1.csv")

list.of.genes %>% filter(gene.name %in% wu.12$Gene)

```

## Sanders, 2013
### Sample Size:
### RNA Source: LCL
### Analysis method: Illumina microarray

```{r echo = FALSE}
sanders.13 <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-schiz/Sanders-2013/sanders-2013-supp-table-1-diff-exprs-schiz.csv")

hits.in.sanders <- list.of.genes %>% filter(gene.name %in% sanders.13$Gene.Abbreviation)

```

## Xiao, 2014

### RNA Source: brain - BA9 and BA24 
```{r echo = FALSE}

xiao.2014.BA9 <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-schiz/xiao-2014/xiao-14-diff-expr-schiz-BA9.csv")

xiao.2014.BA24 <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-schiz/xiao-2014/xiao-14-diff-expr-schiz-BA24.csv")

hits.in.xiao.BA9 <- list.of.genes %>% filter(gene.name %in% xiao.2014.BA9$up | gene.name %in% xiao.2014.BA9$down)

hits.in.xiao.BA24 <- list.of.genes %>% filter(gene.name %in% xiao.2014.BA24$gene.up | gene.name %in% xiao.2014.BA24$gene.down)
```

```{r echo = FALSE}
jalbrzikowski.15.del22q.all <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-autism/jalbrzikowski-2015/jalbrzikowski-2015-table-s2-del22q-all.csv")
jalbrzikowski.15.del22q.all$Symbol <- sub("*","",jalbrzikowski.15.del22q.all$Symbol, fixed = TRUE)

hits.in.jalbrzikowski.del22q.all <- list.of.genes %>% filter(gene.name %in% jalbrzikowski.15.del22q.all$Symbol)

jalbrzikowski.15.del22q.psy <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-autism/jalbrzikowski-2015/jalbrzikowski-2015-table-s3-del22q-psy.csv")
jalbrzikowski.15.del22q.psy$Symbol <- sub("*","",jalbrzikowski.15.del22q.psy$Symbol, fixed = TRUE)

hits.in.jalbrzikowski.del22q.psy <- list.of.genes %>% filter(gene.name %in% jalbrzikowski.15.del22q.psy$Symbol)

jalbrzikowski.15.del22q.asd <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-autism/jalbrzikowski-2015/jalbrzikowski-2015-table-s4-del22q-asd.csv")

jalbrzikowski.15.del22q.asd$Symbol <- sub("*","",jalbrzikowski.15.del22q.asd$Symbol, fixed = TRUE)
hits.in.jalbrzikowski.del22q.asd <- list.of.genes %>% filter(gene.name %in% jalbrzikowski.15.del22q.asd$Symbol)



```

## Zhao, 2015
### Sample Size: 35 SCZ cases and 35 controls.  
### RNASource: brain - anterior cingulated cortext (Brodmann region 24)
### Analysis method: RNASeq
## Study info: post-mortem brain samples from 35 SCZ patients, 35 BPD patients and 35 healthy controls. The brain region used was anterior cingulated cortex (Brodmann region 24), a region known to be involved in learning and executive functions, which are deficit in SCZ patients. Image studies of SCZ patients also showed abnormalities in this region
```{r echo = FALSE}
zhao.2015.schiz <- read.csv("~/LabProjects/GeneExpression/differential-expression-in-schiz/Zhao-2015/zhao-2015-supp-table1-diff-exprs-schiz.csv")

hits.in.zhao <- list.of.genes %>% filter(gene.name %in% zhao.2015.schiz$Gene)
```